Rising from the Ashes II: The Bar-driven Abundance Bimodality of the Milky Way

### 2025-02-18 paper/ms.tex
Update app fig

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{392276_alpha.pdf}
  \caption{\textbf{Bimodality in the abundance plane is linked to distinct epochs separated by quiescence in simulation.} The upper row shows \MgFe{} as a function of age for our subhalo in TNG. The colors indicate stellar populations at fixed values of \FeH{}, which are the same as in Figure~\ref{fig:fig1}. A gap in the relation occurs at an age of approximately $10.6\,\Gyr$, which we indicate with a vertical dashed line. The effect of the $\alpha$-enhancement is clear, as it separates the stars that form before and after this gap in ages (star particles which formed before $z=1.5$ are $\alpha$-enhanced, which occurs at an age of $\sim9.5\,\Gyr$). \edit1{The middle row shows the same TNG and $\alpha$-enhanced TNG data, but with added uncertainties of $12.5\%$ in age and $0.015\,\dex$ in \MgFe{}.} When given these errors, the before and after star particles smear such that the two populations significantly overlap in ages. \edit1{The lower row shows on the left the Milky Way data and on the right the same TNG data with artificial errors but subsampled to the same number of stars older than $5\,\Gyr$ as in the observations (because the simulation sample has almost no star particles younger than $5\,\Gyr$). The limited sample size of the observations makes a direct comparison difficult.}}
  \label{fig:alpha}
\end{figure*}

@@

@@

@@

A complicating factor for this picture comes from the high SFR associated with the galaxy. The depletion time ($M_{\textrm{gas}}/\textrm{SFR}$) at the $t=2.84\,\Gyr$ snapshot is $204\,\Myr$, shorter than the time it takes for the SFR to reach its minimum. This implies the possibility of starvation as a quenching mechanism. However, the average depletion time in the preceding 5 snapshots (which are each $\sim150\,\Myr$ apart) is $220\,\Myr$, so clearly the galaxy is accreting high amounts of gas from its environment. A definitive account, difficult with the current simulation outputs because of its sparse snapshot spacing, requires further work.

@@

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_172175.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for our galaxy of interest at $z=1.5$.}
  \label{fig:app0}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_163071.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app1}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_178140.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app2}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_179009.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app3}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_193025.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app4}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_196834.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app5}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_202467.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app6}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_208267.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app7}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_222555.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app8}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_235345.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app9}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_245661.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app10}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_254663.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app11}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_260347.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app12}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_265671.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app13}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_282632.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app14}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_287601.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app15}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_292983.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app16}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{392276_alpha.pdf}
  \caption{\textbf{Bimodality in the abundance plane is linked to distinct epochs separated by quiescence in simulation.} The upper row shows \MgFe{} as a function of age for our subhalo in TNG. The colors indicate stellar populations at fixed values of \FeH{}, which are the same as in Figure~\ref{fig:fig1}. A gap in the relation occurs at an age of approximately $10.6\,\Gyr$, which we indicate with a vertical dashed line. The effect of the $\alpha$-enhancement is clear, as it separates the stars that form before and after this gap in ages (star particles which formed before $z=1.5$ are $\alpha$-enhanced, which occurs at an age of $\sim9.5\,\Gyr$). \edit1{The middle row shows the same TNG and $\alpha$-enhanced TNG data, but with added uncertainties of $12.5\%$ in age and $0.015\,\dex$ in \MgFe{}.} When given these errors, the before and after star particles smear such that the two populations significantly overlap in ages. \edit1{There is a second population of stars linked to another gap at $\sim8\,\Gyr$, discussed in the text. The lower row shows on the left the Milky Way data and on the right the same TNG data with artificial errors but subsampled to the same number of stars older than $5\,\Gyr$ as in the observations (because the simulation sample has almost no star particles younger than $5\,\Gyr$). The limited sample size of the observations makes a direct comparison difficult.}}
  \label{fig:alpha}
\end{figure*}

@@

\edit1{The upper and middle row shows that there is a potential third population of star particles in the simulation, which is most visible in the $\FeH=-0.25$ and $0\,\dex$ bins (green and red, respectively). A minor gap in the upper panels is present at an age of $\sim8\,\Gyr$, which we discuss further in Section~\ref{ssec:evol}.}

@@

\edit1{There is also a more minor period of quiescence at a cosmic time of $\sim6\,\Gyr$, followed by a period of SF at a much lower rate. This is likely linked to the third population separated by an age gap at $\sim8\,\Gyr$ seen in Figure~\ref{fig:alpha}.}

@@

A complicating factor for this picture comes from the high SFR associated with the galaxy. The depletion time ($M_{\textrm{gas}}/\textrm{SFR}$) at the $t=2.84\,\Gyr$ snapshot is $204\,\Myr$, shorter than the time it takes for the SFR to reach its minimum. This implies the possibility of starvation as a quenching mechanism. However, the average depletion time in the preceding 5 snapshots (which are each $\sim150\,\Myr$ apart) is $220\,\Myr$, so clearly the galaxy is accreting high amounts of gas from its environment. A definitive account, difficult with the current simulation outputs because of its sparse snapshot spacing, requires further work. \edit1{We also delay to future work the cause of the secondary quiescence period at $\sim6\,\Gyr$, briefly discussed in Section~\ref{ssec:evol}.}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{app_392276.pdf}
  \caption{The abundance plane made in a manner similar to Figure~\ref{fig:fig1}. We show }
  \label{fig:app0}
\end{figure*}

\figsetstart
\figsetnum{7}
\figsettitle{Abundance plane for a random subset of sample galaxies in this work.}
\figsetgrpstart
\figsetgrpnum{7.1}
\figsetgrptitle{Abundance plane for subhalo 392276.}
\figsetplot{app_172175.pdf}
\figsetgrpnote{Abundance plane for subhalo 392276.}
\figsetgrpend
\figsetgrpstart
\figsetgrpnum{7.1}
\figsetgrptitle{Abundance plane for subhalo 172175.}
\figsetplot{app_172175.pdf}
\figsetgrpnote{Abundance plane for subhalo 172175.}
\figsetgrpend
\figsetend

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_2.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app1}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_10.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app2}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_143882.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app3}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_167392.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app4}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_289388.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app5}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_300903.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app6}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_348901.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app7}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_398784.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app8}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_404818.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app9}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_425719.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app10}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_439099.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app11}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_465255.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app12}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_494709.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app13}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_510273.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app14}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_547293.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app15}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=\textwidth]{app_576516.pdf}
%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
%   \label{fig:app16}
% \end{figure*}
